Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
add ref to sssec:proc_reg_prompt

Special Processing for short-exposure mini-surveys remains to
be determined.
Since it falls under the remit of Data Management to perform proper calibration,
an evaluatation of whether short exposures for calibration are necessary
will be done. 
If Data Management does find that short-exposure and/or high-sky brightness images
can be processed with reconfigured versions of the LSST Science Pipelines,
then unique and separate data products could be generated with Special Processing.
For the NEO twilight survey, these data products would likely be similar to the
Prompt or DIA data products.
For the calibration survey, these data products would like be similar to the
annual data release tessellated coadds and associated catalog.

>>>>

Special Processing for short-exposure mini-surveys remains to
be determined.
Since it falls under the remit of Data Management to perform proper calibration,
an evaluatation of whether short exposures for calibration are necessary
will be done. 
If Data Management does find that short-exposure and/or high-sky brightness images
can be processed with reconfigured versions of the LSST Science Pipelines,
then unique and separate data products could be generated with Special Processing.
For the NEO twilight survey, these data products would likely be similar to the
Prompt or DIA data products, but note the potential issues with alert
latency from short exposures mentioned in Section~\ref{sssec:proc_reg_prompt}.
For the calibration survey, these data products would like be similar to the
annual data release tessellated coadds and associated catalog.
